Project Uccle

### 2020-06-06 project.Rmd
better R code and add roots plot

```{r diffs/d168-acf-pacf}
plot_grid(
  seis.h.train %>% diff(lag=168) %>%  acf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  seis.h.train %>% diff(lag=168) %>%  acf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  seis.h.train %>% diff(lag=168) %>% pacf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  seis.h.train %>% diff(lag=168) %>% pacf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  nrow = 2
)
```

```{r diffs/d-d168-acf-pacf}
plot_grid(
  seis.h.train %>% diff() %>% diff(lag=168) %>%  acf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  seis.h.train %>% diff() %>% diff(lag=168) %>%  acf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  seis.h.train %>% diff() %>% diff(lag=168) %>% pacf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  seis.h.train %>% diff() %>% diff(lag=168) %>% pacf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  nrow = 2
)
```

>>>>

```{r diffs/d168-acf-pacf}
plot_grid(
  seis.h.train %>% diff(lag=168) %>%  acf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  seis.h.train %>% diff(lag=168) %>%  acf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  seis.h.train %>% diff(lag=168) %>% pacf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  seis.h.train %>% diff(lag=168) %>% pacf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  nrow = 2
)
```

```{r diffs/d-d168-acf-pacf}
plot_grid(
  seis.h.train %>% diff() %>% diff(lag=168) %>%  acf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  seis.h.train %>% diff() %>% diff(lag=168) %>%  acf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  seis.h.train %>% diff() %>% diff(lag=168) %>% pacf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  seis.h.train %>% diff() %>% diff(lag=168) %>% pacf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  nrow = 2
)
```

### 2020-06-06 project.after.Rmd
better R code and add roots plot

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("final.model")) {
  cat(" fitting...")
  final.model <- Arima(final.training, chosen.model[1:3], chosen.model[4:6], lambda=chosen.lambda)
  cat("DONE")
}
if (!exists("final.forecast")) {
  cat(" forecasting...")
  final.forecast <- forecast(final.model, h=168*8, lambda=chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- final.model
plotting.forecast <- final.forecast
cat("AIC =",plotting.model$aic, "\n")
cat("AICc =",plotting.model$aicc, "\n")
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  ,
  residuals.acf
  ,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  ,
  residuals.pacf
  ,
  nrow = 2
))
print(plot_forecast(plotting.forecast) + autolayer(final.testing, series="Original") + ylab("Mean hourly movement (nm)"))
plots <- show_overlap_and_diff(
  final.training, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

>>>>

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("final.model")) {
  cat(" fitting...")
  final.model <- Arima(final.training, chosen.model[1:3], chosen.model[4:6], lambda=chosen.lambda)
  cat("DONE")
}
if (!exists("final.forecast")) {
  cat(" forecasting...")
  final.forecast <- forecast(final.model, h=168*8, lambda=chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- final.model
plotting.forecast <- final.forecast
print(plotting.model)
print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  ,
  residuals.acf
  ,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  ,
  residuals.pacf
  ,
  nrow = 2
))
print(plot_forecast(plotting.forecast) + autolayer(final.testing, series="Original") + ylab("Mean hourly movement (nm)"))
plots <- show_overlap_and_diff(
  final.training, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

### 2020-06-06 project.mems.Rmd
better R code and add roots plot

```{r set mems, include=FALSE}
# MEMS
domain <- c(-7200,7200); pattern <- "MEM.*\\.csv"; name <- "MEM"; description <- "Membach"; proj_file <- 'proj.mems.RData'
```

@@

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6], lambda=train.bc.lambda)
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18, lambda=train.bc.lambda)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  cat("AIC =",plotting.model$aic, "\n")
  cat("AICc =",plotting.model$aicc, "\n")
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
    ,
    residuals.acf
    ,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
    ,
    residuals.pacf
    ,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)"))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

  print(accuracy(plotting.forecast, seis.h.test))
  # qqPlot(plotting.model$residuals, main = paste0("Q-Q plot for ", plotting.forecast$method), xlab = "residuals")
  print(gg_qqplot(plotting.model$residuals) + 
      labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
  )
}

>>>>

```{r set mems, include=FALSE}
# MEMS
domain <- c(-7200,7200); pattern <- "MEMS-.+\\.csv"; name <- "MEM"; description <- "Membach"; proj_file <- 'proj.mems.RData'
```

@@

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6], lambda=train.bc.lambda)
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18, lambda=train.bc.lambda)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)"))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

  print(accuracy(plotting.forecast, seis.h.test))
  print(gg_qqplot(plotting.model$residuals) + 
      labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
  )
}

### 2020-06-06 project.uccs.Rmd
better R code and add roots plot

```{r set uccs, include=FALSE}
# UCCS
domain <- c(-350000,350000); pattern <- "UCCS-.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
```

@@

```{r arima}
to_test <- list(
  #c(0,0,0,0,0,1),  # BAD, Box-Pierce = 0
  #c(0,0,0,0,0,2),  # BAD, Box-Pierce = 0
  #c(0,0,0,0,1,1),  # nice, Box-Pierce = 0
  c(0,0,0,0,1,2),
  #c(0,0,0,0,1,3),  # CAN'T BE DONE: 3*168 = 504 > 350 (limit of arima on r)
  #c(0,1,0,0,0,1),  # BAD, Box-Pierce = 0
  c(0,1,0,0,1,1),
  c(0,1,0,0,1,2),
  c(2,0,0,0,1,0),  # hint from auto.arima D=1
  c(2,0,0,0,1,1),  # after hint from auto.arima D=1
  c(2,1,0,0,1,1),  # after hint from auto.arima D=1 
  c(5,0,0,0,1,0),  # hint from auto.arima D=1
  c(3,1,1,0,1,0),  # hint from auto.arima D=1 d=1
  c(3,1,1,0,1,1),  # after hint then ACF + PACF
  c(4,1,2,0,1,0),  # hint from auto.arima d=1, D=1, max.p=5, max.q=2, max.P=5, max.Q=2, max.order=10
  c(4,1,2,0,1,1)  # after hint then ACF + PACF
)
if (!exists("models")){
  models <- list()
}
for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6])
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18)
    cat("DONE")
  }
  cat("\n")
}
#models[["fitauto"]] <- auto.arima(seis.h.train, D=1, approx=F, trace = T)
#models[["forecastauto"]] <- forecast(models[["fitauto"]], h=168*18)  
#models[["fit311010"]] <- models[["fitauto"]]
#models[["fit412010"]] <- fit
#models[["forecast412010"]] <- forecast(models[["fit412010"]], h=168*18)

@@

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]\n", sep = "")
    if ((fit.name %in% names(models))) {  if ((forecast.name %in% names(models))) {
    plotting.model <- models[[fit.name]]
    plotting.forecast <- models[[forecast.name]]
    cat("AIC =",plotting.model$aic, "\n")
    checkresiduals(plotting.model)
    residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
    residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
    print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
    print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original"))
    plots <- show_overlap_and_diff(
      seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
      base.desc = "training set",
      compare.desc = paste0("refit with ", plotting.forecast$method),
      overlap.ylab = "Mean hourly movement (nm)",
      diff.title = "Difference between ts",
      diff.ylab = "nm", diff.ylab.sec="%",
      diff.ylab.sec.accuracy = .01
    )
    print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

    print(accuracy(plotting.forecast, seis.h.test))
    # qqPlot(plotting.model$residuals, main = paste0("Q-Q plot for ", plotting.forecast$method), xlab = "residuals")
    print(gg_qqplot(plotting.model$residuals) + 
        labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
    )
  }}
}

>>>>

```{r set uccs, include=FALSE}
# UCCS
domain <- c(-350000,350000); pattern <- "UCCS-.+\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
```

@@

```{r arima}
to_test <- list(
  #c(0,0,0,0,0,1),  # BAD, Box-Pierce = 0
  #c(0,0,0,0,0,2),  # BAD, Box-Pierce = 0
  #c(0,0,0,0,1,1),  # nice, Box-Pierce = 0
  c(0,0,0,0,1,2),
  #c(0,0,0,0,1,3),  # CAN'T BE DONE: 3*168 = 504 > 350 (limit of arima on r)
  #c(0,1,0,0,0,1),  # BAD, Box-Pierce = 0
  c(0,1,0,0,1,1),
  c(0,1,0,0,1,2),
  c(2,0,0,0,1,0),  # hint from auto.arima D=1
  c(2,0,0,0,1,1),  # after hint from auto.arima D=1
  c(2,1,0,0,1,1),  # after hint from auto.arima D=1 
  c(5,0,0,0,1,0),  # hint from auto.arima D=1
  c(3,1,1,0,1,0),  # hint from auto.arima D=1 d=1
  c(3,1,1,0,1,1),  # after hint then ACF + PACF
  c(4,1,2,0,1,0),  # hint from auto.arima d=1, D=1, max.p=5, max.q=2, max.P=5, max.Q=2, max.order=10
  c(4,1,2,0,1,1)  # after hint then ACF + PACF
)
if (!exists("models")){
  models <- list()
}

#models[["fitauto"]] <- auto.arima(seis.h.train, D=1, approx=F, trace = T)
#models[["forecastauto"]] <- forecast(models[["fitauto"]], h=168*18)  
#models[["fit311010"]] <- models[["fitauto"]]
#models[["fit412010"]] <- fit
#models[["forecast412010"]] <- forecast(models[["fit412010"]], h=168*18)

@@

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6])
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)"))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

  print(accuracy(plotting.forecast, seis.h.test))
  print(gg_qqplot(plotting.model$residuals) + 
      labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
  )
}
